Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-13 eswc-2012/phdsymp.tex
Tilbakemelding fra Martin
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@78 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
  Federation of semantic data on SPARQL endpoints will allow data to
  remain distributed so that they can be controlled by local curators
  and swiftly updated. There are considerable performance problems,
  intended in the suggested work to be addressed mainly by computation
  and exposure of statistical digests to assist selectivity
  estimation.

  Discontent with current state of the art in benchmarking prompts the
  author to devote much of the time to the evaluation problem and to
  challenge the notion that a ``one-size-fits-all'' benchmark is
  impossible.
\end{abstract}

@@

While the basic feature set of the proposed standard can enable users
to create federated queries, it is not of great use as it requires
extensive prior knowledge of both the data to be queried and
performance characteristics of the involved query engines. Without
this knowledge, the overall performance is insufficient for many
practical applications.

@@

Since the main objective of the proposed work is to create systems
that have sufficient performance for practical applications, it is of
paramount importance to have methodology that can falsify a
hypothesis about an implementation's performance.

@@

However, I have found the current state of the art in benchmarking
lacking in its use of statistics, which motivates two distinct
directions of work: \emph{Statistical experimental planning and execution in
benchmarking} and \emph{statistical methods to optimize SPARQL queries
in a federated regime}.

@@

@@

The contemporary problem in benchmarking is to distinguish
implementations when the measured difference is little or susceptible
to random noise.

@@

When the difference is little, we must consider the possibility that
the measurements are impacted by random noise. Computer systems are
generally very deterministic systems, but there are nevertheless many
such scenarios: The underlying system may be doing other tasks. This
is likely to be particularly important in enterprise environments
where high-load applications are often running on virtual
machines. The garbage collection of some languages may trigger on not
easily foreseeable points. The engine may use randomized algorithms,
or the data may be of such a nature it triggers worst-case behaviour
in situations the query writer cannot foresee. All this contributes to
that we should consider the performance metric, whatever metric is
used, as a \emph{stochastic variable}.

@@

The above relies on that the test data and queries are in fact
representative of the system as a whole. It is often asserted that it
is not possible to create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that the best we can do is to accommodate a
multitude of dimensions and essential challenges in the case of
SPARQL.

>>>>

\begin{abstract}
  Federation of semantic data on SPARQL endpoints will allow data to
  remain distributed so that they can be controlled by local curators
  and swiftly updated. There are considerable performance problems,
  which the present work proposes to address mainly by computation
  and exposure of statistical digests to assist selectivity
  estimation.

  Discontent with current state of the art in benchmarking prompts the
  author to focus on the evaluation problem and to challenge the
  notion that a ``one-size-fits-all'' benchmark is impossible.
\end{abstract}

@@

While the basic feature set of the proposed standard can enable users
to create federated queries, it is not of great use as it requires
extensive prior knowledge of both the data to be queried and
performance characteristics of the involved query engines. Without
this knowledge, the overall performance is insufficient for most
practical applications.

@@

Since the main objective of the proposed work is to create systems
that have sufficient performance for practical applications, it is of
paramount importance to have methodology that can rigorously rank
implementations based on performance.

@@

However, I have found the current state of the art in SPARQL benchmarking
lacking in its use of statistics, which motivates two distinct
directions of work: \emph{Statistical experimental planning and execution in
benchmarking} and \emph{statistical methods to optimize SPARQL queries
in a federated regime}.

@@

Thus, the core problem is: How do we compute and expose a digest that
is of optimal size for the query performance problem?

@@

The contemporary problem in benchmarking is to distinguish
implementations when the measured difference is small or susceptible
to random noise.

@@

When the difference is small, we must consider the possibility that
the measurements are impacted by random noise. Computer systems are
generally very deterministic systems, but there are nevertheless many
such scenarios: The underlying system may be doing other tasks. The
garbage collection of some languages may trigger at not easily
foreseeable points. The engine may use randomized algorithms, or the
data may be of such a nature that it triggers worst-case behaviour in
situations the query writer cannot foresee. All this contributes to
that we should consider the performance metric, whatever metric is
used, as a \emph{stochastic variable}.

@@

The above relies on data and queries that are in fact
representative of the system as a whole. It is often asserted that it
is not possible to create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that the best we can do is to accommodate a
multitude of dimensions and essential challenges in the case of
SPARQL.
